Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-15 paper/abstraction/appendix.tex
more clarifying edits

% n --> m'
% m' --> n

@@

    \vspace{1em}
    We show that $\leq$ forms a simulation relation for the subgraph reachable from $m$ and $m'$ in $PG$ iff $\leq$ forms a simulation relation for the subgraph reachable from $f(m)$ and $f(m')$ for $PG^A$. This involves showing that $m \geq_{rank} m' \iff f(m) \geq_{rank} f(m')$, and that 
    for every transition $\trans{m}{n}{l}$ in $PG$ there is a transition $\trans{m'}{n'}{l}$ iff for every transition $\trans{f(m)}{f(n)}{f(l)}$ in $PG^A$ there is a transition $\trans{f(m')}{f(n')}{f(l)}$.

    \vspace{1em}
    \textbf{Case} $(\Rightarrow)$

    Consider the subgraph of $PG$ reachable from $m$ and $m'$. From $m \leq m'$ and the definition of ($\leq$), we know that $m' \geq_{rank} m$.

    %
    From Lemma 6, and $m' \geq_{rank} m$ we know that $f_{pg}(m') \geq_{rank} f_{pg}(m)$. 
    From Lemma 8, there is a transition $\trans{f(n)}{f(n')}{f(l)}$.

    \vspace{1.2em}
    \textbf{Case} $(\Leftarrow)$

    Let $M = f(m)$ and let $M' = f(m')$.
    Suppose that $M \leq M'$, which means that with $M' \geq_{rank} M$ in the abstract product graph. It also means that, for each neighbor $N'$, if we have the transition: $\trans{M'}{N'}{L}$ then we also have a transition: $\trans{M}{N}{L}$ where $N' \geq_{rank} N$. We must show that the same relation holds for $m$ and $m'$.

    \vspace{1em}
    Assume that $\Topo(M) = f(a)$ and $\Topo(N) = f(b)$. Also assume that $m'$ has a neighbor $n'$. We know that $\Topo(m) = a$ and $\Topo(m') = b$. Clearly $(a,b)$ is a valid concrete topology edge since it is a transition in the product graph between $m$ and $m'$. We now apply Lemma 7 with the following facts:

@@

    Lemma 7 lets us conclude that there exists a node $n'$ such that:

    \[ \begin{array}{ll}
      1. & \Topo(n) = b \\
      2. & f_{pg}(n) = N \\
      3. & (m,n) ~\text{is an edge in}~ PG \\
      4. & \Rank(n) = \Rank(N) \\
    \end{array} \]

    Thus if there is transition $\trans{m'}{n'}{b}$, then there is also a transition $\trans{m}{n}{b}$. Lemma 6 together with the assumption $N' \geq N$ shows that $n' \geq{rank} n$.

@@

The previous lemma tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.

\begin{defn}
  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
  Clearly from Lemma 9, $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
\end{defn}

@@

  For concrete ($PG$) and abstract ($PG^A$) product graphs related by $f_{pg}$

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow [~ ma~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~ pin = \mathit{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(BS,q_N) ~\vert~ BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \}, BS \neq \emptyset  \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \mathit{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{ b ~\vert~ (b,q_n) \in pin\}, bs \neq \emptyset \}), \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathit{adjOut}(PG,m) \}, \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A(f_{pg}(m)) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
  \end{array} \]%

@@

    Suppose for node $M$, there exists a node $m=(l,q_m)$ such that $f_{pg}(m) = M$. 
    We observe the following superset relation:
    %
    $$\{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG,m)\} \subseteq \{ b ~\vert~ (b,l) \in G.E \}$$
    %
    This is trivially true from the definition of the product graph. Any product graph edge will correspond to a topology edge. The following inequality will also hold:
    %
    $$\{b ~\vert~ b \in f^{-1}(B),~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \} \supseteq \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
    %
    Since whenever $(b,q_N) \in adjIn(PG,m)$ it must be the case that $(B,q_N) \in adjIn(PG^A, f_{pg}(m))$ by the homomorphism, and because $f^{-1}(B) \supseteq \{ b \}$. By combining these observations, we can conclude the following:
    %
    $$\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \}$$
    is equivalent to
    $$\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
    %
    The same reasoning can be applied to adjOut as well. 
    Further, note that because we are looking at a particular location $l$, there can only be at most one such $m = (l,q_N)$ such that $f_{pg}(m) = M = (f(l), q_N)$ since the automata are deterministic. 
    %
    This means that $M \leftarrow (l,q_M) \in PG^A$ can be replaced with $m \leftarrow (l,q_m) \in PG$ since for each $M$ we will either have some $m$ such that $f_{pg}(m) = M$ and the above equivalence holds, or else there is no such $M$, in which case the set is filtered by the condition: $BS \neq \emptyset$.

@@

  \vspace{.4em}
  \textbf{Case} ($t = pfx$)
  \vspace{.4em}

@@

@@

@@

      \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (\Con(in,\ell,\Gamma,f,G),q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \Con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \ell,\Gamma,f,G), \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), true, \ell, \Gamma, f, G) ~] ~] ~] \\
  \end{array} \]%

@@

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\Con(\{B ~\vert~ (B,q_N) \in pin \}, \ell, \Gamma, f, G), BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \Con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \ell,\Gamma,f,G), \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), true, \ell, \Gamma, f, G) ~] ~] ~] \\
  \end{array} \]%

@@

  From Lemma 10, this is equivalent to the following:

@@

    \[
    \begin{array}{llll}
      & & \Compile(\Con(p,\Gamma,f),G) \\
      &=& \Compile(\Con(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, \Gamma,f), G) 
            & \text{Substitution} \\
      &=& \Compile([pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(l) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n, \Gamma,f) \cap \EndR(l) ~\vert~ (pfx,l) \in \Gamma(x)], G) 
            & \text{Definition of con} \\
      &=& \CompileMbgp([\CompilePg(pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(l) ~\Prefer~ \\
      & & ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \ldots ~\Prefer~ \\ 
      & & ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \Con(r_n, \Gamma,f) \cap \EndR(l),G) ~\vert~ (pfx,l) \in \Gamma(x)]) 
            & \text{Definition of compile} \\

@@

    \noindent
    As before, we now show that the right hand side is equivalent by applying the definitions of $\Con$ and $\Compile$:

        \[
    \begin{array}{llll}
      & & \Con(\Compile(p,G^A),\Gamma,f,G) \\
      &=& \Con(\Compile(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A),\Gamma,f,G)
            & \text{Substitution} \\
      &=& \Con(\CompileMbgp([\CompilePg(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A)]),\Gamma,f,G)
            & \text{Definition of Compile} \\
      &=& \Con(\CompileMbgp([(\$x,PG^A,\Pref^A)]),\Gamma,f,G)
            & \text{Assumption}\\
    \end{array}
    \]

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x),
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), \Gamma, f, G) ~] ~] ~] \\
  \end{array} \]%

@@

  After filtering the cases where $in = \{ start \}$ and $l' \neq \ell$, we have the same situation as the previous case. 
  This works because each $PG_{i}$ was constructed from $con(r_{i}, \ell, \Gamma, f, G) \cap end(l_{i})$. This means that the only state in $PG_{i}$ connected to the start node ($\mathit{start}$) is a node for $l_{i}$. This was ensured by the fact that the transition function for each regular expression $\sigma_{i}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{i} \}$ from the construction of the automata.

@@

    \vspace{.5em}
    \noindent
    Given a policy $pol = p_1, \ldots, p_n$ we apply Theorem 11 after rewriting the policy. For the left side:
    \[
    \begin{array}{llll}
      & & \Con(\Compile(pol,G^A),\Gamma,f,G) \\
      &=& \Con(\Compile(p_1, \ldots, p_n, G^A),\Gamma,f,G) & \text{Substitution} \\
      &=& \Con(\CompileMbgp([\CompilePg(p_1), \ldots, \CompilePg(p_n)]),\Gamma,f,G)
            & \text{Definition of Compile} \\
      &=& \Con(\CompileMbgp([(t_1,PG^A_1,\Pref^A_1), \ldots, (t_n,PG^A_n,\Pref^A_n)]),\Gamma,f,G)
            & \text{Assumption}\\
    \end{array}
    \]

@@

    \noindent
    First, we observe that, for each $p_i$, Theorem 11 and $\CompilePg$ give us that, for each $i$:
    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), \\ 
     ~~~~~~~~~~~~ rc = [\CompilePred((t_i, PG^A_i, \Pref^A_i))] ~~] \\
    \end{array} \]%

    \noindent
    Is equivalent to:

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), \\ 
     ~~~~~~~~~~~~ rc = [\CompilePred((t'_i, PG_i, \Pref_i))] ~~] \\
    \end{array} \]%

    \noindent
    By applying the definition of $\CompileMbgp$, we need to show:

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), \\ 
     ~~~~~~~~~~~~ rc = append_{i \in \{1..n\}}(\CompilePred((t_i, PG^A_i, \Pref^A_i))) ~] \\
    \end{array} \]%

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), \\ 
     ~~~~~~~~~~~~ rc = append_{i \in \{1..n\}}(\CompilePred((t'_i, PG_i, \Pref_i))) ~] \\
    \end{array} \]%

    \noindent
    Clearly this follows by the definition of list $\mathrm{append}$

>>>>

@@

    \vspace{1em}
    \noindent
    We show that $\leq$ forms a simulation relation for the subgraph reachable from $m$ and $m'$ in $PG$ iff $\leq$ forms a simulation relation for the subgraph reachable from $f(m)$ and $f(m')$ for $PG^A$. This involves showing that $m \geq_{rank} m' \iff f(m) \geq_{rank} f(m')$, and that 
    for every transition $\trans{m}{n}{l}$ in $PG$ there is a transition $\trans{m'}{n'}{l}$ iff for every transition $\trans{f(m)}{f(n)}{f(l)}$ in $PG^A$ there is a transition $\trans{f(m')}{f(n')}{f(l)}$.

    \vspace{1em}
    \noindent
    \emph{Case} $(\Rightarrow)$

    \vspace{.4em}
    Consider the subgraph of $PG$ reachable from $m$ and $m'$. From $m \leq m'$ and the definition of ($\leq$), we know that $m' \geq_{rank} m$.

    \noindent
    From Lemma 6, and $m' \geq_{rank} m$ we know that $f_{pg}(m') \geq_{rank} f_{pg}(m)$. 
    From Lemma 8, there is a transition $\trans{f(n)}{f(n')}{f(l)}$.

    \vspace{1.2em}
    \noindent
    \emph{Case} $(\Leftarrow)$

    \vspace{.4em}
    Let $M = f(m)$ and let $M' = f(m')$.
    Suppose that $M \leq M'$, which means that with $M' \geq_{rank} M$ in the abstract product graph. It also means that, for each neighbor $N'$, if we have the transition: $\trans{M'}{N'}{L}$ then we also have a transition: $\trans{M}{N}{L}$ where $N' \geq_{rank} N$. We must show that the same relation holds for $m$ and $m'$. 
    %
    Assume that $\Topo(M) = f(a)$ and $\Topo(N) = f(b)$. Also assume that $m'$ has a neighbor $n'$. We know that $\Topo(m) = a$ and $\Topo(m') = b$. Clearly $(a,b)$ is a valid concrete topology edge since it is a transition in the product graph between $m$ and $m'$. We now apply Lemma 7 with the following facts:

@@

    \noindent
    Lemma 7 lets us conclude that there exists a node $n$ such that:

    \[ \begin{array}{ll}
      1. & \Topo(n) = b \\
      2. & f_{pg}(n) = N \\
      3. & (m,n) ~\text{is a concrete edge in}~ PG \\
      4. & \Rank(n) = \Rank(N) \\
    \end{array} \]

    \noindent
    Thus if there is transition $\trans{m'}{n'}{b}$, then there is also a transition $\trans{m}{n}{b}$. 
    Lemma 6 together with the assumption $N' \geq_{rank} N$ and the fact that $\Rank(n) = \Rank(N)$ lets us conclude that $n' \geq_{rank} n$.

@@

\vspace{1em}
Lemma 9 tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
We use this fact to define the local preference function ($\Pref : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $\Pref(m) = \Pref(f(m))$ for all product graph nodes $m$.

\vspace{1em}
\begin{defn}
  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers starting from 0 according to the total ordering for $\leq$.
  From Lemma 9, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$.
\end{defn}

@@

  For concrete ($PG$) and abstract ($PG^A$) product graphs related by $f_{pg}$, if $f(\ell) = \Topo(M)$, then

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow [~ ma~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~ pin = \mathrm{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(BS,q_N) ~\vert~ BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \}, BS \neq \emptyset  \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \mathrm{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \mathrm{adjIn}(PG,m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{ b ~\vert~ (b,q_n) \in pin\}, bs \neq \emptyset \}), \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathrm{adjOut}(PG,m) \}, \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A(f_{pg}(m)) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
  \end{array} \]%

@@

    Suppose for node $M$, there exists a node $m=(l,q_m)$ such that $f_{pg}(m) = M$. 
    We want to show the following:
    %
    %$$\{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG,m)\} \subseteq \{ b ~\vert~ (b,l) \in G.E \}$$
    %
    %This is trivially true from the definition of the product graph. Any product graph edge will correspond to a topology edge. The following inequality will also hold:
    %
    %$$ \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\} \subseteq \{b ~\vert~ b \in f^{-1}(B),~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \}$$
    %
    %Since whenever $(b,q_N) \in adjIn(PG,m)$ it must be the case that $(B,q_N) \in adjIn(PG^A, f_{pg}(m))$ by the homomorphism, and because $f^{-1}(B) \supseteq \{ b \}$. By combining these observations, we can conclude the following:
    %
    $$\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \mathrm{adjIn}(PG^A,f_{pg}(m)) \}$$
    is equivalent to
    $$\{ b ~\vert~ (b,q_N) \in \mathrm{adjIn}(PG,m)\}$$
    %
    Suppose that an element $x \in \{ b ~\vert~ (b,q_N) \in \mathrm{adjIn}(PG,m)\}$. Then $(b,q_N) \in \mathrm{adjIn}(PG,m)$ and there is an edge $(b,\ell)$ in the topology between $b$ and $\Topo(m)$. From the homomorphism, this means $(f(b),q_N) \in \mathrm{adjIn}(PG^A,f(m))$. It follows that $x \in \{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \mathrm{adjIn}(PG^A,f_{pg}(m)) \}$.

    \vspace{1em}
    \noindent
    Now suppose the other direction. There is an element $x \in \{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \mathrm{adjIn}(PG^A,f_{pg}(m)) \}$. We know that $f(x) = B$, and that there is a topology edge between $b$ and $\ell$. Lemma 7 together with the fact that $f(\ell) = \Topo(m)$ lets us conclude that there is an edge in the concrete $PG$ between $(b,q_N)$ and $m$. It follows then that $x \in \{ b ~\vert~ (b,q_N) \in \mathrm{adjIn}(PG,m)\}$.

    \vspace{1em}
    \noindent
    The same reasoning can be applied to adjOut as well. Further, note that because we are looking at a particular location $l$, there can only be at most one such $m = (l,q_N)$ such that $f_{pg}(m) = M = (f(l), q_N)$ since the automata are deterministic. 
    %
    This means that $M \leftarrow (l,q_M) \in PG^A$ can be replaced with $m \leftarrow (l,q_m) \in PG$ since for each $M$ we will either have some $m$ such that $f_{pg}(m) = M$ and the above equivalence holds, or else there is no such $M$, in which case the set is filtered by the condition: $BS \neq \emptyset$.

@@

  \vspace{.4em}
  \noindent
  \textbf{Case} ($t = pfx$)
  \vspace{.4em}

@@

    \vspace{1em}
    \noindent
    \textbf{(Right-hand side)}

@@

    \vspace{1em}
    \noindent
    \textbf{(Left-hand side)}

@@

      \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (\Con(in,\ell,\Gamma,f,G),q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \Con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \ell,\Gamma,f,G), \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~] \\
  \end{array} \]%

@@

    \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\Con(\{B ~\vert~ (B,q_N) \in pin \}, \ell, \Gamma, f, G), BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \Con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \ell,\Gamma,f,G), \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~] \\
  \end{array} \]%

@@

  Applying Lemma 10 with the fact that $f(\ell) = l = \Topo(M)$ this is equivalent to the following:

@@

    \vspace{1em}
    \noindent
    \textbf{(Right-hand side)}
    %
    \[
    \begin{array}{llll}
      & & \Compile(\Con(p,\Gamma,f),G) \\
      &=& \Compile(\Con(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, \Gamma,f), G) 
            & \text{Substitution} \\
      &=& \Compile([pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(l) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n, \Gamma,f) \cap \EndR(l) ~\vert~ (pfx,l) \in \Gamma(x)], G) 
            & \text{Definition of con} \\
      &=& \CompileMbgp([\CompilePg(pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(l) ~\Prefer~ \\
      & & ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \ldots ~\Prefer~ \\ 
      & & ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \Con(r_n, \Gamma,f) \cap \EndR(l),G) ~\vert~ (pfx,l) \in \Gamma(x)]) 
            & \text{Definition of compile} \\

@@

    \noindent
    As before, we now show that the left hand side is equivalent by applying the definitions of $\Con$ and $\Compile$:

    \vspace{1em}
    \noindent
    \textbf{(Left-hand side)}
    %
    \[
    \begin{array}{llll}
      & & \Con(\Compile(p,G^A),\Gamma,f,G) \\
      &=& \Con(\Compile(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A),\Gamma,f,G)
            & \text{Substitution} \\
      &=& \Con(\CompileMbgp([\CompilePg(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A)]),\Gamma,f,G)
            & \text{Definition of Compile} \\
      &=& \Con(\CompileMbgp([(\$x,PG^A,\Pref^A)]),\Gamma,f,G)
            & \text{Assumption}\\
    \end{array}
    \]

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), \Gamma, f, G) ~] ~] ~] \\
  \end{array} \]%

@@

  After filtering the cases where $in = \{ G.start \}$ and $l' \neq \ell$, we have the same situation as the previous case. 
  However, we know that each $PG_{i}$ was constructed from $con(r_{i}, \ell, \Gamma, f, G) \cap end(l_{i})$. This means that the only state in $PG_{i}$ connected to the start node ($\mathit{start}$) is a node for $l_{i}$. This was ensured by the fact that the transition function for each regular expression $\sigma_{i}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{i} \}$ from the construction of the automata. We apply Lemma 10 with the fact that $f(\ell) = \Topo(M)$:

@@

    \vspace{.5em}
    \noindent
    The proof simply uses Theorem 11 after rewriting the policy according to $\Con$ and $\Compile$.
    Given a policy $pol = p_1, \ldots, p_n$ we apply Theorem 11 after rewriting the policy. For the left side:
    \[
    \begin{array}{llll}
      & & \Con(\Compile(pol,G^A),\Gamma,f,G) \\
      &=& \Con(\Compile(p_1, \ldots, p_n, G^A),\Gamma,f,G) & \text{Substitution} \\
      &=& \Con(\CompileMbgp([\CompilePg(p_1, G^A), \ldots, \CompilePg(p_n, G^A)]),\Gamma,f,G)
            & \text{Definition of Compile} \\
      &=& \Con(\CompileMbgp([(t_1,PG^A_1,\Pref^A_1), \ldots, (t_n,PG^A_n,\Pref^A_n)]),\Gamma,f,G)
            & \text{Assumption}\\
    \end{array}
    \]

@@

    \vspace{1em}
    \noindent
    \textbf{(Given)}

    \noindent
    First, we observe that, for each $p_i$, Theorem 11 and $\CompilePg$ give us that, for each $i$:

    \[
    \begin{array}{lll}
    &   \Con([~ l \rightarrow rc ~\vert~ l \in internal(G^A.V), rc = 
        [\CompilePred((t_i, PG^A_i, \Pref^A_i))] ~~], \Gamma,f,G)     & \text{Left side} \\
    = & [~ l \rightarrow rc ~\vert~ l \in internal(G.V), rc = 
        [\Con(\CompilePred((t_i, PG^A_i, \Pref^A_i)), \Gamma,f,G)] ~~] & \text{Definition of con} \\
    = & [~ l \rightarrow rc ~\vert~ l \in internal(G.V), rc = [\CompilePred((t'_i, PG_i, \Pref_i))] ~~]
        & \text{Right side} \\
    \end{array}
    \]

    \vspace{1em}
    \noindent
    \textbf{(To Show)}

    \vspace{.4em}
    \noindent
    By applying the definition of $\CompileMbgp$, we start with the left hand side:

    \[ \begin{array}{l}
     ~~~~~ \Con([~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~~~~~ l \in internal(G^A.V), \\ 
     ~~~~~~~~~~~~~~~~ rc = append_{i \in \{1..n\}}(\CompilePred((t_i, PG^A_i, \Pref^A_i))) ~], \Gamma,f,G) \\
    \end{array} \]%

    \noindent
    By applying the definition of $\Con$ to the left-hand side, we get:

    \[ \begin{array}{l}
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~~~~ l \in internal(G.V), \\ 
     ~~~~~~~~~~~~ rc = \Con(append_{i \in \{1..n\}}(\CompilePred((t_i, PG^A_i, \Pref^A_i))), \Gamma,f,G)  ~]\\
    \end{array} \]%

    \noindent
    Applying the definition of $\Con$ one more time:
